---
title: "eds221-day5"
---

## Testing Code

R package for unit test: testthat

expect_equal(): does the function return expected values?

expect_type(): does the function return the expected type?

expect_length(): if a vector is returned, is it the expected length?

expect_true(): does the function return TRUE?

## Let's think of some tests:

```{r}
# function provided
fish_mass <- function(alpha, beta, fish_length) {
  if (fish_length <= 0) {
    stop("Fish length must be greater than 0.")
  }
  mass <- alpha * (fish_length ^ beta)
}
```

```{r}
library(testthat)
# example of a unit test for fish_mass()

# if you're expecting a length of 1, you can use this code:
testthat::expect_length(fish_mass(alpha = 1, beta =2, fish_length = 3), 1)

# this would return an error because you're expecting a length of 2
testthat::expect_length(fish_mass(alpha = 1, beta =2, fish_length = 3), 2)
```

# CRAN Packages

CRAN Task view: https://cran.r-project.org/web/views/

ROpenSci: https://ropensci.org/

Checklist for choosing between R packages in ecology and evolution: https://onlinelibrary.wiley.com/doi/full/10.1002/ece3.5970

```{r}
# to cite
# in R:
# citation("packagename")
```
